Sound Automated Synthesis of Digital Controllers

### 2016-10-08 paper/paper.tex
remove Figure 1

In this paper, however, we explore the automatic synthesis of 
{\em correct-by-construction} dgital controllers, which 
reduces the deveopment cost and design time for a number of models.  
In particular, we are interested in synthesising controllers 
for {\em hybrid closed-loop systems}, {\it i.e.}, embedded controllers along with a model of their
physical environment, the plant, as shown in
Fig.~\ref{fig:closed-system}, that are {\em stable}.  Due to the complexity
of such systems, we focus on linear models with known configurations
to perform parametric synthesis of the controller dynamics.

@@

\begin{figure}
\centering
\resizebox{.35\textwidth}{!}{
 \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
     semithick, initial text=, ampersand replacement=\&,]

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.5cm, column sep=.5cm] {
   \coordinate (aux0);
   \& \node[circle] (circle) {}; 
   \& \node[fill=yellow!20] (da) {{\sc D/A}}; 
   \& \node[fill=yellow!20] (p) {{\sc P}};
   \& \node[fill=yellow!20] (ad) {{\sc A/D}}; 
   \& \coordinate (aux1);\\
   \& \coordinate (aux3); 
   \&
   \&
   \node[fill=yellow!20] (c) {C};
   \& 
   \& \coordinate (aux2);\\
  };

  \path[->] (aux0) edge (circle.west);
  \path  
   (circle.east) edge (da.west)
   (da.east) edge (p.west)
   (p.east) edge (ad.west)
   (ad.east) edge (aux1.west)
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (c.east)
   (c.west) edge (aux3.east); 
  \path[->]  (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Closed-Loop System. \label{fig:closed-system}}
\end{figure}

@@

This intermediate ANSI-C code model $(\tilde C(z),\mathfrak{G}(z),\phi)$
containing a specification $\phi$ for the verification properties ({\it i.e.}, robust stability)
is translated into SAT/SMT formulae by a back-end model-checking tool ({\it e.g.},
CBMC~\cite{ClarkeKL04} or ESBMC~\cite{CordeiroFM12}).
If any property violation is found, then DSVerifier reports a
counterexample, which contains system inputs or parametric deviations
$\Delta{G}$ that lead the system to a failure.  A successful verification
result is reported if the system is safe with respect to $\phi$.  In
particular, the stability verification is complete and sound, since it does
not depend on system inputs and outputs.
In the case of stability, the specification $\phi$ consists in a number of assumptions
on the polynomial coefficients, following Jury's Criteria, as well as the restrictions
set in the representation of these coefficients by the function $f$ (Eq. \ref{FWL_tf}).

>>>>

In this paper, however, we explore the automatic synthesis of 
{\em correct-by-construction} dgital controllers, which 
reduces the deveopment cost and design time for a number of models.  
In particular, we are interested in synthesising controllers 
for {\em hybrid closed-loop systems}, {\it i.e.}, embedded controllers along with a model of their
physical environment (the plant), which are {\em stable}.  Due to the complexity
of such systems, we focus on linear models with known configurations
to perform parametric synthesis of the controller dynamics.

@@

%\begin{figure}
%\centering
%\resizebox{.35\textwidth}{!}{
% \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
%     semithick, initial text=, ampersand replacement=\&,]

%  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.5cm, column sep=.5cm] {
%   \coordinate (aux0);
%   \& \node[circle] (circle) {}; 
%   \& \node[fill=yellow!20] (da) {{\sc D/A}}; 
%   \& \node[fill=yellow!20] (p) {{\sc P}};
%   \& \node[fill=yellow!20] (ad) {{\sc A/D}}; 
%   \& \coordinate (aux1);\\
%   \& \coordinate (aux3); 
%   \&
%   \&
%   \node[fill=yellow!20] (c) {C};
%   \& 
%   \& \coordinate (aux2);\\
%  };

%  \path[->] (aux0) edge (circle.west);
%  \path  
%   (circle.east) edge (da.west)
%   (da.east) edge (p.west)
%   (p.east) edge (ad.west)
%   (ad.east) edge (aux1.west)
%   (aux1.south) edge (aux2.north)
%   (aux2.west) edge (c.east)
%   (c.west) edge (aux3.east); 
%  \path[->]  (aux3.north) edge (circle.south);
% \end{tikzpicture}
%}
% \caption{Closed-Loop System. \label{fig:closed-system}}
%\end{figure}

@@

This intermediate ANSI-C code model $(\tilde C(z),\mathfrak{G}(z),\phi)$
containing a specification $\phi$ for the verification properties ({\it i.e.}, robust stability)
is translated into SAT/SMT formulae by a back-end model-checking tool ({\it e.g.},
CBMC~\cite{ClarkeKL04} or ESBMC~\cite{CordeiroFM12}).
If any property violation is found, then DSVerifier reports a
counterexample, which contains system inputs or parametric deviations
$\Delta{G}$ that lead the system to a failure.  A successful verification
result is reported if the system is safe with respect to $\phi$.  In
particular, the stability verification is complete and sound, since it does
not depend on system inputs and outputs.
In the case of stability, the specification $\phi$ consists in a number of assumptions
on the polynomial coefficients, following Jury's Criteria, as well as the restrictions
set in the representation of these coefficients by the function $f$ (cf. Eq. \eqref{FWL_tf}).
